SMASH companion code resources

### 2018-11-06 analysis/index.Rmd
wflow_publish("index.Rmd")

@@

+ [Illustration of SMASH on "spikes" data set.](spikesdemo.html)

@@

>>>>

This repository contains source code and data accompanying our manuscript,

> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
signals.* [arXiv:1709.10066](http://arxiv.org/abs/1605.07787).

The new methods can be found in the [smashr package][smashr].

@@

The following analyses generate some of the empirical results
presented in [Xing & Stephens (2016)][smashr-preprint]. If you
encounter a problem running any of the R code in these examples,
please post an [issue][issues].

+ [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)

@@

## Citing this work

If you find any of the source code in this repository useful for your
work, please cite our paper:

> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
> Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
> signals.* [arXiv:1709.10066][smash-preprint].

## License

Copyright (c) 2016-2018, Zhengrong Xing, Peter Carbonetto & Matthew
Stephens.

All source code and software in this repository are made available
under the terms of the [MIT license][mit-license]. See the
[LICENSE](LICENSE) file for the full text of the license.

## Credits

This project was developed by [Zhengrong Xing][zhengrong] at the
University of Chicago, with support and contributions from
[Peter Carbonetto][peter] and [Matthew Stephens][matthew].

[smashr]: https://github.com/stephenslab/smashr
[smash-preprint]: http://arxiv.org/abs/1605.07787
[issues]: https://github.com/stephenslab/smash-paper/issues
[mit-license]: https://opensource.org/licenses/mit-license.html
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu
